---
title: "Task7"
author: "Cole Hon"
date: "9/19/2022"
output: 
  html_document:
    keep_md: TRUE
editor_options: 
  chunk_output_type: console
---

```{r}
library(ggplot2)
library(readr)
library(knitr)
library(tidyverse)
library(dplyr)
library(forcats)
library(downloader)
library(knitr)
```


```{r Read in Data}
download.file("https://raw.githubusercontent.com/hadley/r4ds/master/data/heights.csv", "height", mode = "wb")

heightdata <- read_csv("height")
head(heightdata)
```



```{r Create HeightEd data set}
HeightEd <- heightdata %>%
  mutate( ed = fct_collapse(as.factor(ed),
          primary = c("3","4","5","6"),
          secondary = c("7","8","9","10","11"),
          highschoolgrad = c("12"),
          associate = c("13","14","15"),
          bachelors = c("16"),
          mastersdoctorate = c("17","18")
  ))

head(HeightEd)
```



```{r Relationship between Education and Race}

ggplot(data = HeightEd) + 
  geom_bar(mapping = aes(x = ed, fill = race), position = "dodge") +
  labs(x = "Education Level",
       y = "Amount of People",
       title = "Relationship between Race and Level of Education")


```



```{r Relationship between sex and education}
ggplot(data = HeightEd) + 
  geom_bar(mapping = aes(x = ed, fill = sex), position = "dodge") +
  labs(x = "Sex",
       y = "Amount of People",
       title = "Relationship between Sex and Level of Education")


```




```{r My own grpahic}
  
ggplot(data = HeightEd, mapping = aes(x = ed, 
                                  y = earn, 
                                  color = sex,
                                  shape = sex)) +
  geom_point() +
  labs(x = "Education Level",
       y = "Income", 
       title = "Earnings by Level of Education based off of Sex") + 
  annotate("text", x = "highschoolgrad", y = 150000, label = "A majority of the education levels consists of a male being the highest earner", size = 2.7)
  
```
The graph I produced wasn't exctly how I envisioned it would turn out, but it effectively communicates the message I want to deliver: The largest income in a majority of the different education levels completed belongs to a male. That message is evident in my visualization by looking at the highest point for each education level, and it is also stated on the graph. Placing the annotation on the graph was trickier than I expected it to be, as I had to keep changing the x cooridnate to make sure the text wasn't coming off of the graph. I also had to keep adjusting the size of the text to find the best fit. 


