---
title: "Task 4"
author: "Cole Hon"
date: "9/8/2022"
output:
  html_document:
    theme: cosmo
    keep_md: true
editor_options: 
  chunk_output_type: console
---

```{r Load Packages}
library(tidyverse)
```

```{r Read in Data & Create a Table}
iris_data <- iris 
tibble(iris_data)
```

```{r Arrange the iris data by Sepal.Length & display first 10 rows}
arrange_Sepal.Length <- arrange(iris_data, Sepal.Length)
head(arrange_Sepal.Length, 10)
```

```{r Select Species and Petal.Width }
testdat <- select(iris_data, Species, Petal.Width)
testdat
```

```{r Create a new table called species_mean that has the mean for each variable for each Species}
species_mean <- group_by(iris_data, Species)
species_mean <- summarize(species_mean, v1 = mean(Sepal.Length), v2 = mean(Sepal.Width),
                          v3 = mean(Petal.Length),
                          v4 = mean(Petal.Width))
species_mean
```

```{r Create iris_min with only the observations with at least 3 for Sepal.Width and not 2.5 for Petal.Width}
iris_min <- filter(iris_data, Sepal.Width >= 3, Petal.Width != 2.5)
iris_min
```


```{r Create Iris_size}
iris_size <- iris_data %>%
  mutate(Sepal.Size = 
           case_when(
             Sepal.Length < 5 ~ "small",
             Sepal.Length >= 5 & Sepal.Length < 6.5 ~ "medium",
             Sepal.Length >= 6.5 ~ "large"))
head(iris_size)
```


```{r Creating Iris Rank}
iris_rank <- arrange(iris_data, desc(Petal.Length))
mutate(iris_rank, rank=min_rank(Petal.Length))

```


```{r Use summarize_all()}
?summarize_all
means_sd_species <- iris_data %>%
  group_by(Species) %>%
  summarize_all(list(Mean=mean, Std_dev = sd))
means_sd_species

```

Novel Questions
Q1: How has the housing market changed in the past 30 years?
Q2: Is youth football decresing in participation?
Q3: Which U.S. state would be ideal to HQ a business?

Feedback from 5-10 people
My first two questions recived positive feedback. Whether it was becuase of sole intrerest or applicable use, it was commonly said that I should pursue those first two questions. Feedback said that my first question was pretty broad in regards to application for that question. I know i personally wouldn't be starting a business anytime soon.

Professional Feedback
My first question would be very intsresting to pursue being that I will eventually be in the market to buy a house. It is good to educated myself on a topic that is considered one of the bigger life decisions. 
