---
title: "Task11"
author: "Cole Hon"
date: "10/3/2022"
output:
  html_document:
    keep_md: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(knitr)
```

```{r}
f <- tempfile()
download.file("https://raw.githubusercontent.com/fivethirtyeight/data/master/fandango/fandango_score_comparison.csv", "f")

score <- read_csv("f")
str(score)
head(score)


```


```{r}
ratings <- score %>%
  select(FILM, Fandango_Ratingvalue, RT_norm_round, Metacritic_norm_round, IMDB_norm_round) %>%
  pivot_longer(2:5, names_to = "Website", values_to = "Rating") %>%
  select(FILM, Website, Rating)
```


```{r}
t40 <- head(ratings, n = 40)
```


```{r}
ggplot(data = t40, aes(x = Website, y = Rating, fill = Rating)) +
  geom_col(position = "dodge") +
  facet_wrap(~ FILM, nrow = 2) +
  theme_bw() +
  theme(legend.position = 'none') +
  labs(x = "Rating",
       y = "Film")
```

I know the task said to make it show the first 20 rows, but i chose to do the first 40 beacuse I felt like comparing the ratings from the different sources of 10 movies is more accurate than just 5 movies. With that being said, by looking at the charts created, i'd say that Fandago & RT have the same ratings for movies while metacritic and IMBD generally will have the same ratings for movies.






