---
title: "CaseStudy6"
author: "Cole Hon"
date: "10/3/2022"
output:
  html_document:
    keep_md: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(knitr)
library(dplyr)
library(gridExtra)
?diamonds
head(diamonds)
```


```{r}
#Diamond Length (x)
ggplot(data = diamonds, aes(x)) +
  geom_histogram(fill = 'cyan', color = 'Black') +
  xlim(3,10) +
  theme_bw() +
  labs(x = "Length (mm)",
       y = "Amount of Length Observations",
       title = "Diamond Lengths")
```


```{r}
#Diamond Width (y)
ggplot(data = diamonds, aes(y)) +
  geom_histogram(fill = 'deeppink', color = 'black') +
  xlim(3,10) +
  theme_bw() +
  labs(x = "Width (mm)",
       y = "Amount of Width Observations",
       title = "Diamond Widths")
```



```{r}
#Diamond Depth (z)
ggplot(data = diamonds, aes(z)) +
  geom_histogram(fill = 'chartreuse', color = 'black') +
  xlim(1,7) +
  theme_bw() +
  labs(x = "Depth (mm)",
       y = "Amount of Depth Observations",
       title = "Diamond Depths")
```


```{r}
#Exploring distributiuon of Prices
ggplot(data = diamonds, aes(price)) +
  geom_histogram(fill = 'green', color = 'black') +
  theme_bw() +
  labs(x = "Price ($)",
       y = "Amount of Price Observations",
       title = "Diamond Prices")
```

Nothing really sticks out to  me about this graph. It is expected that there are more cheaper diamonds then therre are expensive diamonds, following the idea of supply and demand. Since there are probably a large amount of diamonds of "poor quality" (even though metrics for "quality" isn't included in on this graph), they will generally be cheaper. 

```{r}
ggplot(data = diamonds, aes(x = cut, y = price)) +
  geom_boxplot() +
  theme_bw() +
  labs(x = "Cut",
       y = "Price",
       title = "Price V. Cut")
```

```{r}
ggplot(data = diamonds, aes(x = carat, y = price)) +
  geom_point() +
  theme_bw() +
  labs(x = "Carat",
       y = "Price",
       title = "Price V. Carat")
```


```{r}
ggplot(data = diamonds, aes(x = color, y = price)) +
  geom_boxplot() +
  theme_bw() +
  labs(x = "Color",
       y = "Price",
       title = "Price V. Color")
```


```{r}
ggplot(data = diamonds, aes(x = clarity, y = price)) +
  geom_boxplot() +
  theme_bw() +
  labs(x = "Clarity",
       y = "Price",
       title = "Price V. Clarity")
```

```{r}
ggplot(diamonds, aes(cut, carat)) +
  geom_boxplot() +
  theme_bw() +
  labs(x = 'Cut',
       y = 'Carat', 
       title = 'Diamond Cut vs. Carat')
```


First observation: Carats seems to be what effects the price of a diamond the most.

Second Observation: There are less carats in higher cuts of diamonds. Cut seems to be the driving facotr of what makes a diamond more expensive or not. 


```{r}
diamonds %>%
  mutate(price_part =
           case_when(
             price >= 0 & price <= 2500 ~ '0-2500',
             price >= 2501 & price <= 5000 ~ '2501-5000',
             price >= 5001 & price <= 7500 ~ '5001-7501',
             price >= 7501 & price <= 10000 ~ '7501-10000',
             price >= 10001 & price <= 12500 ~ '10001-12500',
             price >= 12501 & price <= 15000 ~ '12501-15000',
             price >= 15001 & price <= 17500 ~ '15001-17500',
             price >= 17501 & price <= 20000 ~ '17501-20000',
             price >= 20001 & price <= 22500 ~ '20001-22500',
             price >= 22501 & price <= 25000 ~ '22501-25000'),
         price_part =  fct_relevel(price_part,'0-3000','2501-5000','5001-7501','7501-10000','10001-12500','12501-15000','15001-17500','17501-20000','20001-22500','22501-25000')) %>%
  ggplot(aes(carat, price, fill = price_part)) +
    geom_boxplot() +
    scale_fill_brewer(palette = 'Reds') +
    labs(x = 'Carat', y = 'Price ($USD)', title = 'Carat grouped by Price', fill = "Price Ranges") +
    theme_bw()
```



```{r}
diamond_p <- diamonds %>%
  mutate(price_groups = 
           case_when(
             price >= 0 & price <= 2000 ~ "1-2000",
             price >= 2001 & price <= 4000 ~ "2001-4000",
             price >= 4001 & price <= 6000 ~ "4001-6000",
             price >= 6001 & price <= 8000 ~ "6001-8000",
             price >= 8001 & price <= 10000 ~ "8001-10000",
             price >= 10001 & price <= 12000 ~ "10001-12000",
             price >= 12001 & price <= 14000 ~ "12001-14000",
             price >= 14001 & price <= 16000 ~ "14001-16000",
             price >= 16001 & price <= 18000 ~ "16001-18000",
             price >= 18001 & price <= 20000 ~ "18001-20000"))
         
ggplot(data = diamond_p, aes(carat, fct_reorder(price_groups, carat), fill = price_groups)) +
  geom_boxplot() +
  theme_bw() +
  labs(x = "Carat",
       y = "Price",
       title = ("Price Groups of Different Carats")) +
  theme(legend.position = 'none')
```


```{r}
large <- diamonds %>%
  filter(carat >= 4.01)

largeplot <- ggplot(data = large, aes(x = price)) +
  geom_histogram(fill = 'yellow', color = 'black') +
  theme_bw() +
  labs(x = "Price",
       y = "Amount of Large Diamonds",
       title = "Prices of Large Carat Diamonds")

small <- diamonds %>%
  filter(carat <= 1.2)

smallplot <- ggplot(data = small, aes(x = price)) +
  geom_histogram(fill = 'purple', color = 'black') +
  theme_bw() +
  labs(x = "Price",
       y = "Amount of Small Diamonds",
       title = "Prices of Small Carat Diamonds")

grid.arrange(largeplot, smallplot, nrow = 1)
```
As expected, the price of large diamonds is higher than the price of small diamonds. With that being said, there is a much higher amount of small diamonds (44784) than there are large diamonds (5), so there is a much larger price range of those smaller diamonds than there are of the large diamonds.



```{r}
ggplot(diamonds, aes(x = carat, y = price, fill = cut)) +
    geom_col(alpha = 1) +
    coord_cartesian(xlim = c(0,4), ylim = c(0, 2600000), expand = FALSE) +
    facet_wrap(~cut, scales = 'free') +
    labs(x = 'Carat', y = 'Price ($)', title = 'Price of Carats by Type of Cut') +
    theme_bw() 
```

