---
title: "Task 2"
author: "Cole Hon"
date: "8/30/2022"
output: 
  html_document:
    theme: cosmo
    keep_md: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Loading Knitr}
install.packages("knitr")
library(knitr)
library(tidyverse)
```

```{r Tasks 2}
sin(pi/4)
```
Using R as a calculator

```{r Assinging X}
x <- 10/3

```
names can only contain numbers, letters, "_", and "."
Names that cannot be assigned:
Cole#Hon
Cole Hon
Cole!Hon



```{r Sequence}
MySequence <- seq(1,50, length.out = 7)
MySequence
```
Assigning a sequence to an operator


```{r Vector}
my_vector <- c(1, 5, 12, 31, 19)

```
Vector assigned to "my_vector" using the c



```{rDeterming Results}
7 + 5 == 12

```
the "==" makes the statement true to whatever follows in regards to what came before it

```{r}
(7 + 4 = 12) | (5 - 4 = 1)
```
Results in an error because the "=" does not atcually mean equals/true, more specifically it is not the appropriate assignment operator. 

```{r Exercise 1}
my_variable <- 10
my_varıable
#> Error in eval(expr, envir, enclos): object 'my_varıable' not found

```
Why does this not work?
the second my_variable is spelled wrong, it consists of the wrong type of i


```{r Exercise 2}
library(tidyverse)

ggplot(dota = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))

fliter(mpg, cyl = 8)
filter(diamond, carat > 3)
```

Spelling errors. "dota" should be "data" & "fliter" should be "filter"
"cyl = 8" needed to be changed to "cyl == 8"
"diamond" needed to be chnaged to "diamonds"


```{r Exercise 2 Continued}

ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy))

filter(mpg, cyl == 8)
filter(diamonds, carat > 3)
```

Exercise 3

Pressing "Alt Shift K" brought up a menu woth keyboard short cuts.You can also get to this menu by clicking "Tools" followed by "keyboard shortcuts help".


