---
title: "Task17"
author: "Cole Hon"
date: "11/2/2022"
output:
  html_document:
    keep_md: TRUE
    code_folding: 'hide'
---


```{r}
library(tidyquant)
library(knitr)
library(lubridate)
library(tidyverse)
library(timetk)
library(dygraphs)
```

Stocks I chose:
- Adidas (ADDYY)
- Nike (NKE)
- Under Armour (UAA)

Stocks my friend chose:
- Amazon (AMZN)
- Apple (AAPL)
- Microsoft (MSFT)


### Pulling Price Performance Data
```{r}
(Microsoft <- tq_get("MSFT", get = "stock.prices"))
(Apple <- tq_get("AAPL", get = "stock.prices"))
(Amazon <- tq_get("AMZN", get = "stock.prices"))

(Adidas <- tq_get("ADDYY", get = "stock.prices"))
(Nike <- tq_get("NKE", get = "stock.prices"))
(UnderArmour <- tq_get("UAA", get = "stock.prices"))
```


### Combining Data
```{r}
MyStock <- tq_get(c("AAPL", "AMZN", "MSFT"), get = "stock.prices", from = "2021-10-1", to = today())
head(MyStock)
tail(MyStock)

FriendStock <- tq_get(c("ADDYY", "NKE", "UAA"), get = "stock.prices", from = "2021-10-1", to = today())
head(FriendStock)
tail(FriendStock)


Both <- tq_get(c("AAPL", "AMZN", "MSFT", "ADDYY", "NKE", "UAA"), get = "stock.prices", from = "2021-10-1", to = today())
head(Both)
tail(Both)
```


#Comparing Stock Prices Visualization
```{r}
stockplot <- Both %>%
  ggplot(aes(x = date, y = close, color = symbol)) +
  geom_line() +
  labs(title = "Friends Choosing Between Stocks", y = "close price", x = "") +
  theme_tq()

stockplot
```


### Comparing Stock percentages interavtive visualization
```{r}
adjusted <- Both %>%
  select(symbol, date, adjusted) %>%
  pivot_wider(names_from = symbol, values_from = adjusted) %>%
  tk_xts(date_var = date)

dygraph(adjusted, main = "Friends Comparing Stocks") %>%
  dyRebase(percent = TRUE) %>%
  dyShading(from = "2021-10-01", to = today()) %>%
  dyRangeSelector()
```

The stocks I chose to go with were ones I felt were pretty popular, falling in the retail or technoloy sectors of types of stocks. I also use products of these companies on a daily basis, so I thought it'd be interesting to see how they've been doing on the market. The first visualization I made was a line graph plotting the prices of each stock over the selected time period. This visualization gives a good idea on how each stock has performed compared to each other, but it didn't exactly give specifics. To get the specific information I wanted, I created a dygrpah. This interactivce graph was much better for comparioson puproses as it gave the net gain/loss as a percentage for each stock overtime. The graph shows that Apple was the only company with a net gain, as all the others showed an overall decrease in stock value over the selected time frame. 






