---
title: "CaseStudy 11"
author: "Cole Hon"
date: "11/15/2022"
output:
  html_document:
    keep_md: TRUE
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(ggplot2)
library(readr)
library(knitr)
library(dplyr)
library(forcats)
library(downloader)
library(tidyquant)
library(dygraphs)
library(scales)
library(tidyverse)
library(maps)
library(ggsflabel)
library(devtools)
library(remotes)
library(stringr)
library(leaflet)
library(mapview)
```


### Import Data
```{r}
permit_data <- tempfile()
download("https://raw.githubusercontent.com/WJC-Data-Science/DTS350/master/permits.csv", permit_data, mode = "wb")
PA_permits <- read_csv(permit_data)

penn <- read.csv('latlong.csv')
head(penn)

```

### Clean Data
```{r}
PApermits <- PA_permits %>%
  filter(StateAbbr == "PA", year==2010)

permits <- PApermits %>%
  mutate(county = as.character(county))

head(permits)

pa <- penn %>%
  mutate(county = as.character(County.Code.Number))

```


```{r}
combined <- left_join(pa,permits, by='county') %>%
  drop_na()
head(combined)
```

```{r}
data1 <- combined %>%
  arrange(desc(value))
```


```{r}
data1$quartile <- ntile(data1$value,4)
data1$quartile
```

```{r}
topcounty <- data1 %>%
  filter(row_number() == 1)
```


```{r}
ntile4 <- data1 %>%
  filter(quartile == 4)
ntile3 <- data1 %>%
  filter(quartile == 3)
ntile2 <- data1 %>%
  filter(quartile == 2)
ntile1 <- data1 %>%
  filter(quartile == 1)
```


```{r}
leaflet() %>%
  addTiles() %>%
  addCircleMarkers(data = ntile4,
                   radius = 7,
                   color = "blue",
                   stroke = FALSE,
                   fillOpacity = 1,
                   popup = ~county,
                   label = ~value) %>%
    addCircleMarkers(data = ntile3,
                   radius = 7,
                   color = "red",
                   stroke = FALSE,
                   fillOpacity = 1,
                   popup = ~county,
                   label = ~value)%>%
    addCircleMarkers(data = ntile2,
                   radius = 7,
                   color = "darkblue",
                   stroke = FALSE,
                   fillOpacity = 1,
                   popup = ~county,
                   label = ~value) %>%
    addCircleMarkers(data = ntile1,
                   radius = 7,
                   color = "green",
                   stroke = FALSE,
                   fillOpacity = 1,
                   popup = ~county,
                   label = ~value) %>%
    addCircleMarkers(data = topcounty,
                   radius = 7,
                   color = "royalblue1",
                   stroke = FALSE,
                   fillOpacity = 1,
                   popup = ~county,
                   label = ~value)
```

In this case study, I used the leaflet package to make an interactive map of pennsylvania. I selected the amount of building permits in each county, and then divided them up by using the ntile function into 4 separate groups based on the amount of permits each county holds. One group is the bottom 25th percentile, the 25-50th percentile, the 50-75th percentile, and the top 25th percintile. The percentiles the counties fall in are represented on the map by diffferent colors. I used a sepreate color for the top count, which is the one I suiggegested my friend moves to.