---
title: "CaseStudy4"
author: "Cole Hon"
date: "9/20/2022"
output:
  html_document: 
  keep_md: TRUE
  code_folding: 'hide'
editor_options: 
  chunk_output_type: console
---

```{r}
library(tidyverse)
library(readr)
library(knitr)
library(downloader)
library(lubridate)
library(dplyr)
library(ggplot2)
library(forcats)
```


```{r}
library(nycflights13)
?flights
head(flights)
```


2. Which origin airport is best to minimize my chances of a late arrival when I am using Delta Airlines?

```{r Delta Airlines}
delay <- flights %>%
  filter(carrier == "DL", arr_delay > 0) %>%
  group_by(origin) %>%
  count()
delay

delay_plot <- ggplot(data=delay, mapping=aes(origin, n, fill=origin)) +
  geom_bar(stat="identity", position="dodge")+
  labs(y = "Amount of Delays",
       x = "Flight Origin",
       title = "Amount of Delayed Delta Flights at Airport of Origin") +
  theme(legend.position = "none")
delay_plot
```
From my findings, the best origin airport to fly from to avoid a late arrival when using Delta would be EWR. This is because EWR has the least amount of delayed origin flights, which can result in the least amount of late arrivals.



3. Which destination airport is the worst airport for arrival time?

```{r}
d_delay <- flights %>%
  group_by(dest) %>%
  summarise(median_delaytime = mean(arr_delay, na.rm = TRUE)) %>%
  filter(median_delaytime > 25)
d_delay
destplot <- ggplot(data=d_delay, mapping=aes(dest, median_delaytime, color=dest)) +
  geom_point() +
  labs(y = "Median Delay Time",
       x = "Destination Airport",
       title = " Top Median Delay Times for Destination Airports (> 25 minutes)") +
  theme(legend.position = "none")
destplot
```

The metric I decided to use when figuring the wprst airport for arrival time was the median delay time. I went with median delay time becuase I didn't want any outliers to skew the average delay time. I honed in on any delay over 25 minutes to be a non-desirable delay time. The results pulled in 4 airports with a median arrival delay time being more than 25 minuites, with CAE coming in with the highest median delay time at right under 45 minutes.
